\chapter[Multiple Choice PartII]{SAT Writing Multiple Choice Part II}
\section{SAT Worksheet 1B: Warm-up}
\textit{Directions: Below is a list of topics most frequently tested on the Sentence Error Identification Questions and the Sentence Improvement Questions. Circle the topic(s) that you find the most challenging.} 

\bigskip
\begin{center}
\begin{multicols}{2}
\textbf{\underline{Error Identification}}

Subject-verb agreement\\
Pronoun reference\\
Parallelism\\
Adverbs vs. Adjectives\\
Tenses\\
Singular-Plural Noun Inconsistency\\
Comparatives vs. Superlatives\\
Sentence Fragments\\
Shift in Point of View\\
You and Me Errors\\
Idioms\\
Redundancy\\
Word Choice\\
Hypothetical Statements

\columnbreak
\textbf{\underline{Sentence Improvements}}\\
Subject-Verb Agreement\\
Pronoun Reference\\
Run-ons\\
Modifiers\\
Parallelism\\
Shift in Point of View\\
You and Me Errors\\
Idioms\\
Redundancy\\
Hypothetical Statements\\
Sentence fragments\\
\end{multicols}
\end{center}

\bigskip
\textbf{Then, go to the sentence error questions in the writing section that you did for homework. For each question that you got incorrect or left blank, label the type of error for that question.}

\vfill
\newpage

\section[Multiple Choice Strategies]{Strategies and Practice for SAT writing Multiple Choice}

We will now focus on strategy and practice for the sentence error identification and sentence improvement questions. 

\bigskip

The most commonly tested and missed grammar points can be seen below. When you are answers sentence error or improvement questions, BE A CYCLOPS and always be keep one eye open for these most commonly missed grammar points.

\bigskip
\textbf{B is for “being”:} The word “being” is commonly heard in speech but does not usually make for the best sentences.

\bigskip
\textbf{E is for agrEEmEnt:} Identify the subject and the verb that is associated with the subject. The verb needs to match the subject in number and gender. This means that the subject and the main verb need to be both singular or both plural. 

\bigskip

\bigskip
\textbf{A is for awful verb tense:} Check when the action is happening and then if the given verb tense can be used to describe the time period that the action is happening. 

\bigskip

\bigskip
\textbf{C is for clause (aka commas towards the beginning of the sentence):} Clauses at the beginning of sentences have a description, then a comma, then more words. The description must be describing the first word after the comma. 

\bigskip
\textbf{Y is for you, me, and other pronouns:} If “you” is not in the underlined section, then it must be paired with “you” in the underlined section. If “one” or “someone” is not in the underlined section, then it must be paired with you in the underlined section. Also, make sure that pronouns like “it” or “they” clearly refer to the subject of the sentence. 

\bigskip
\textbf{C if for contrasts and other conjunction/connectors:} Words like “and” are used to add another idea, however, words like “but” are used to show differences between things. 

\bigskip
\textbf{L is for list:} If there is a list, all of the words must be the same part of speech and the same verb tense. 

\bigskip
\textbf{O is for “of” and commas that might separate the subject and the verb:} The verb ending is dependent on the singularity or plurality of the subject.

\bigskip
\textbf{P is for preposition:} Make sure the preposition matches the word before it. To combat this, learn your idioms!

\bigskip
\textbf{S is for short:} Is the sentence as short as it can be without changing the meaning? 

\newpage
\section[Sentence Error]{Strategy for Sentence Error Multiple Choice Questions}

Your goal on the sentence errors is to determine whether or not there is an error in the sentence. If so, then you must mark the error.

\begin{enumerate}
\item{Read through the sentence. If you clearly hear an error, then mark it. On sentence errors, you are done.}
\vfill\item{If you can't hear an error, check for the errors listed in SAT Writing section Part I and also the errors in BE A CYCLOPS. If you see one of those points that are incorrect, then mark it.} 
\vfill\item{Many students get nervous when they can't find an error. They are unsure of whether there is an error or if the entire sentence is correct. Remember, answer choice, “E”, no error, is the correct answer in approximately 20\% of the questions. To feel better about choosing “E”, we recommend going through each of the blanks and labeling the grammar point covered. For example, if the word “you” is underlined, then the grammar point tested is probably pronouns. Then, remind yourself of this grammar rule and ask yourself if it is properly executed. If so, then move on to the next one. If you finish answer choice “D” and there is still no errors, then “E” is most likely your answer choice.}
\end{enumerate}

\vfill\textit{You should use these steps on the practice questions on the following pages.}
\newpage

\section[Sentence Error Practice]{SAT Worksheet 2B: Sentence Error Practice Questions}
\textit{Directions: Read the question and circle the underlined portion that contains an error. If there's an error, identify the error (for example, a clause error) and then write a correction to the error in the space around the question. Note: On the real SATs, you will just need to circle the error rather than describing the error type and making a correction to the incorrect underlined portion.}

\bigskip
\centerline{\textbf{Sentence Error Questions}}

\bigskip
Directions: Read the question and circle the underlined portion that contains an error. If there's an error, identify the error (for example, a clause error) and then write a correction to the error in the space around the question. Note: On the real SATs, you will just need to circle the error rather than describing the error type and making a correction to the incorrect underlined portion.

\begin{enumerate}
\item 

\begin{inparaenum}[A]
\tfrac{During}{\item} my \tfrac{last}{\item} vacation, I \tfrac{came across}{\item} a beautiful public garden \tfrac{wandering}{\item} in the historic district of the city. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill\item 

\begin{inparaenum}[A]
At the open mic night, Jeff \tfrac{enjoyed listening to}{\item} his friend Kristin's songs, \tfrac{which he}{\item} thought were \tfrac{more original}{\item} \tfrac{than the other singers}{\item}. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill\item

\begin{inparaenum}[A]
Dog psychology, \tfrac{a field that}{\item} investigates \tfrac{the reasons for}{\item} the behavior of dogs, \tfrac{help}{\item} trainers both understand dogs and prevent \tfrac{their problems}{\item}. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill\item

\begin{inparaenum}[A]
\tfrac{By the time}{\item} Noah finally \tfrac{arrived at}{\item} the theater, we \tfrac{waited}{\item} for him for half an hour, \tfrac{missing}{\item} the beginning of the movie. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill\item

\begin{inparaenum}[A]
Famous for \tfrac{their}{\item} bright blue feet, the blue-footed booby \tfrac{is}{\item} a marine bird that \tfrac{lives}{\item} on islands in the Pacific Ocean, \tfrac{most notably}{\item} on the Galapagos. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill
\newpage\item

\begin{inparaenum}[A]
Both her sense of humor \tfrac{and}{\item} her dedication \tfrac{to providing}{\item} extra help to students \tfrac{has}{\item} gained Ms. Nicholson the \tfrac{respect of}{\item} the students and faculty. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill\item

\begin{inparaenum}[A]
Many famous actors are \tfrac{motivated by}{\item} either love of their craft \tfrac{and}{\item} personal talent, but \tfrac{some seem}{\item} interested \tfrac{only in money}{\item}. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill\item

\begin{inparaenum}[A]
It is \tfrac{much easier}{\item} to tie a shoe \tfrac{than explaining}{\item} in words \tfrac{exactly how}{\item} a shoe \tfrac{is tied}{\item}. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill\item

\begin{inparaenum}[A]
My \tfrac{boss's}{\item} intense preoccupation \tfrac{on}{\item} procedure \tfrac{leaves}{\item} little room \tfrac{for}{\item} innovation or creativity. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill\item

\begin{inparaenum}[A]
\tfrac{Throughout}{\item} the book, the protagonist's \tfrac{constant}{\item} changing beliefs \tfrac{made him}{\item} a confusing and unpredictable character \tfrac{with no}{\item} core sense of identity. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill
\newpage
\item

\begin{inparaenum}[A]
Apparently \tfrac{impressed with}{\item} our resumes, \tfrac{the company}{\item} decided to hire both \tfrac{Isabel and I}{\item} to manage \tfrac{its network of}{\item} campaign headquarters throughout the city. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill\item

\begin{inparaenum}[A]
Jean Rhys, \tfrac{whose}{\item} Dominican background \tfrac{has influenced}{\item} her writing, \tfrac{describes}{\item} many details of life in the Caribbean Islands \tfrac{vividly}{\item} in her novels and short stories. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill\item

\begin{inparaenum}[A]
Because he \tfrac{is home sick}{\item} when his coworkers planned out \tfrac{their}{\item} vacation days, he \tfrac{is worried}{\item} that \tfrac{he missed}{\item} out on his preferred schedule. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill\item

\begin{inparaenum}[A]
\tfrac{Also recommended}{\item} by my professor \tfrac{was}{\item} several well-known books \tfrac{and}{\item} a recent editorial \tfrac{in}{\item} The New York Times. \tfrac{No Error}{\item}
\end{inparaenum}

\vfill\item

\begin{inparaenum}[A]
The project Alex and his group \tfrac{are presenting}{\item}, a PowerPoint prepared by \tfrac{he and three others,}{\item} \tfrac{is}{\item} the \tfrac{culmination of}{\item} a month of research and preparation. \tfrac{No Error}{\item}
\end{inparaenum}
\end{enumerate}
\vfill
\pagebreak

\section[Sentence Improvement]{Strategy for Sentence Improvements}
Your goal on the sentence errors is to choose the best sentence out of the 5 answer choices. Some answer choices may be technically correct, but only one choice is “the best”. This will be the one that is the most clear (no grammatical errors) and concise. 

\begin{center}
\begin{enumerate}
\item{Read through the sentence. If you clearly hear an error, then circle it (e.g. if the verb tense is wrong, circle the verb).Think about what you would do to change the error. }
\item{Scan through the answer choices to see if how you would change it is a choice. If so, read the full sentence with the underlined portion you just selected in the sentence. If the full sentence makes sense, select it and move on to the next question. }
\item{If you know there is an error but aren't sure what it is, read through the answer choices and eliminate ones that don't make sense. Then, read the full sentence with the underlined portion for each sentence. Mark the best answer choice and move on to the next question.} 
\item{If you don't know whether or not there is an error, check for the errors listed in the SAT Writing Section Part I and also in the BE A CYCLOPS acronym.\\
Select the correction and read the full sentence to make sure it makes sense and contains the original meaning of the sentence.  Then move on to the next question.  }
\item{If you still have no idea, then skip the question. You can come back to it at the end of the section or leave it blank (remember, because you get deducted points for getting a question wrong, it can be advantageous to skip a handful of questions that you do not know for each section. }
\end{enumerate}
\end{center}

\bigskip
\textit{You should use these steps on the practice questions on the following page.}
\pagebreak

\section[Sentence Improvement Practice]{SAT Worksheet 3B Sentence Improvement Practice Questions}
\textit{Directions: Read the question. If there's an error, identify the type of error (for example, a clause error). If you think the original phrasing produces a better sentence than any of the other alternatives, select choice A; if not, select one of the other choices.}

\begin{enumerate}
\item Derry Hall is \underline{older than it but still just as comfortable as Nicholson Hall.}

\begin{enumerate}[label=(\Alph*)]
\item{older than it but still just as comfortable as Nicholson Hall.}
\item{older than Nicholson Hall but just as comfortable.}
\item{older than Nicholson Hall; it is just as beautiful as it.}
\item{older and it is just as comfortable as Nicholson Hall.}
\item{just as comfortable as Nicholson Hall and it is older than it.}
\end{enumerate}

\bigskip
\item To complete the degree, a student must present a thesis, oral presentation, \ul{and writing a creative piece.}

\begin{enumerate}[label=(\Alph*)]
\item and writing a creative piece
\item and a creative piece.
\item and to write a creative piece.
\item and with a creative piece.
\item and creative piece.
\end{enumerate}

\bigskip
\item \underline{In similarity with} some other popular blogs, the \textit``Happiness Project" asks its readers to contribute personal stories and opinions.
\begin{enumerate}[label=(\Alph*)]
\item In similarity with
\item As
\item Like
\item Like the case with
\item Like what happened with
\end{enumerate}

\newpage
\item The travel guide is useful because it offers not just reviews and photos, \ul{but also tells you what and how to get to various destinations.}
\begin{enumerate}[label=(\Alph*)]
\item but also tells you what and how to get to various destinations.
\item but also they gives ways of getting to various destinations.
\item but also advice of what and how to get to various destinations.
\item but also tells you what to do and how to get to various destinations.
\item and also tells you what to do and how to get to various destinations.
\end{enumerate}

\bigskip
\item Karen Russell wrote the bestseller \textit{Swamplandia} \underline{and she was twenty-four years old then.}
\begin{enumerate}[label=(\Alph*)]
\item and she was twenty-four years old then.
\item upon the reaching of twenty-four years.
\item at age twenty-four years old.
\item when she was twenty-four.
\item at the time of being twenty-four.
\end{enumerate}

\bigskip
\item \underline{I am skilled at writing presentations, however, I have trouble with public speaking.}
\begin{enumerate}[label=(\Alph*)]
\item I am skilled at writing presentations, however, I have trouble with public speaking.
\item I am skilled at writing presentations, I have trouble with public speaking.
\item I am skilled at writing presentations; however, I have trouble with public speaking.
\item I am skilled at writing presentations: however, I have trouble with public speaking.
\item I am skilled at writing presentations, along with public speaking giving me trouble.
\end{enumerate}

\newpage
\item \ul{Education and computer programming are an example of a growing field with relative job security.}
\begin{enumerate}[label=(\Alph*)]
\item Education and computer programming are an example of a growing field with relative job security.
\item Education and computer programming exemplifies a growing field with relative job security.
\item Education and computer programming are examples of growing fields with relative job security.
\item Education and computer programming are an example of growing fields with relative job security. 
\item Education and computer programming exemplify a growing field with relative job security.
\end{enumerate}

\bigskip
\item Mr. Smith tends to praise essays that align with his own \ul{opinions, and it is rare for good grades to be given to essays with opposing ideas.}
\begin{enumerate}[label=(\Alph*)]
\item opinions, and it is rare for good grades to be given to opposing ideas.
\item opinions, it is rare for good grades to be given to essay with opposing ideas.
\item opinions and rarely gives good grades to essays with opposing ideas.
\item opinions and he rarely gives good grades to essays with opposing ideas.
\item opinions, although rarely giving good grades to essay with opposing ideas.
\end{enumerate}

\newpage
\item Sloths descend from their homes in the tops of trees once a \ul{week, they are risking being eaten by ground predators in the rainforest.}
\begin{enumerate}[label=(\Alph*)]
\item week, they are risking being eaten by ground predators in the rainforest.
\item week, likewise they risk being eaten by ground predators in the rainforest.
\item week, risking them to be eaten by ground predators in the rainforest.
\item week; the risk is to be eaten by ground predators in the rainforest.
\item week, at the risk of being eaten by ground predators in the rainforest.
\end{enumerate}

\bigskip
\item A mix of poetry, stream of consciousness, and radio transcripts, the novels of Hunter S. Thompson were more experimental \underline{than many of his contemporaries.}
\begin{enumerate}[label=(\Alph*)]
\item than many of his contemporaries.
\item than those of many of his contemporaries.
\item than many of his contemporaries, as far as novels are concerned.
\item than that of many of his contemporaries.
\item than was most of his contemporaries.
\end{enumerate}

\bigskip
\item Confident that she was fully prepared, Sarah spent the night before her SATs relaxing \underline{but not to be doing more practice problems.}
\begin{enumerate}[label=(\Alph*)]
\item but not to be doing more practice problems.
\item and not to be doing more practice problems.
\item rather than doing more practice problems. 
\item rather than having done more practice problems.
\item more than to do more practice problems.
\end{enumerate}

\bigskip
\item Traveling through the Southwest, \underline{we photographed the desert, cacti, and rock formations.}
\begin{enumerate}[label=(\Alph*)]
\item we photographed the desert, cacti, and rock formations.
\item the desert, cacti, and rock formations were the subject of our photographs.
\item we photographed the desert, cacti, and also the rock formations.
\item the desert, cacti, and rock formations, which we photographed.
\item what we photographed was the desert, cacti, and rock formations.
\end{enumerate}

\newpage
\item Neil deGrasse Tyson, American astrophysicist, author, and science communicator, \ul{and who presented} Cosmos: A Spacetime Odyssey, a television series based on Carl Sagan's Cosmos: A Personal Voyage.
\begin{enumerate}[label=(\Alph*)]
\item and who presented
\item he presented
\item and who is presenting
\item and having acted as presenter for
\item presented
\end{enumerate}

\bigskip
\item Lincoln gave the Gettysburg Address in 1863 \underline{with his purpose being to honor} the soldiers who had died there in battle.
\begin{enumerate}[label=(\Alph*)]
\item with his purpose being to honor
\item and his purpose was honoring
\item he honored
\item to honor
\item thus honored
\end{enumerate}

\bigskip
\item \ul{Because of their ability to scare off other wolves and large animals, our early ancestors started living together with wolves, eventually turning them into the many different species of domesticated dogs we know today.}

\begin{enumerate}[label=(\Alph*)]
\item Because of their ability to scare off other wolves and large animals, our ancestors started living together with wolves, eventually turning them into the many different species of domesticated dogs we know today.
\item Because of their ability to scare off other wolves and large animals, so our ancestors started living together with wolves, eventually turning them into the many different species of domesticated dogs we know today.
\item Our early ancestors started living with wolves because of their ability to scare off other wolves and large animals.  They eventually turned them into the many different species of domesticated dogs we know today.
\item They have the ability to scare off other wolves and large animals, so our early ancestors started living together with wolves, and eventually turned them into the many different species of domesticated dogs we know today.
\item Wolves can scare off other wolves and large animals, because of this our early ancestors started living with  them, eventually turning them into the many different species of domesticated dogs we know today.
\end{enumerate}

\newpage
\item The survival of many species and ecosystems depends on the creation and enforcement of environmental regulations, the cooperation of national \ul{governments, and individuals need to make efforts of individuals to live in sustainable, environmentally-friendly ways.}

\begin{enumerate}[label=(\Alph*)]
\item governments, and individuals need to make efforts of individuals to live in sustainable, environmentally-friendly ways.   
\item governments, in combination with individuals needing to make efforts to live sustainable, environmentally-friendly ways.
\item governments, while also individuals are making efforts to live in sustainable, environmentally-friendly ways.
\item governments, and the efforts of individuals who are trying to be living in a sustainable, environmentally-friendly way.
\item governments, and the efforts of individuals to live in sustainable, environmentally-friendly ways.   
\end{enumerate}

\bigskip
\item To start our research project, our group gathered books, articles, and other materials \ul{and distributed them equally between John, Isabelle, and I.}

\begin{enumerate}[label=(\Alph*)]
\item and distributed them equally between John, Isabelle, and I.
\item and distributed them equally between John, Isabelle, and me.
\item while distributing them equally between John, Isabelle, and I.
\item to distribute them equally between John, Isabelle, and I.
\item and being for the purpose to distribute them equally between John, Isabelle, and me.
\end{enumerate}

\bigskip
\item \ul{Finding the subject fascinating, all the classes in the philosophy department were taken by James.}
\begin{enumerate}[label=(\Alph*)]
\item Finding philosophy fascinating, all the classes in that department were taken by James.
\item The subject is fascinating and is why James took all the classes in the philosophy department.
\item Finding the subject fascinating, James took all the classes in the philosophy department.
\item The subject can be found fascinating, and this made James take all the classes in the philosophy department.
\item James found the subject fascinating, he took all the classes in the philosophy department.
\end{enumerate}

\newpage
\item \underline{Being as she is a talented singer}, Theresa has great technical range and emotional depth.

\begin{enumerate}[label=(\Alph*)]
\item Being as she is a talented singer
\item In being a talented singer
\item Although she is a talented singer
\item A talented singer
\item Singing with a lot of talent
\end{enumerate}

\bigskip
\item The beneficial physical and mental effects of regular exercise \ul{is well-documented and widely-reported.} 
\begin{enumerate}[label=(\Alph*)]
\item is well-documented and widely-reported.
\item has been well-documented and widely-reported.
\item are well-documented and widely-reported.
\item is being well-documented and widely-reported.
\item has been documented well and reported widely.
\end{enumerate}

\bigskip
\item \underline{For as many as ten years and more} Grace worked as a professional dancer.
\begin{enumerate}[label=(\Alph*)]
\item For as many as ten years and more
\item For not much more than about ten years 
\item For a little over ten years and more
\item For ten years and then some
\item For more than ten years
\end{enumerate}

\bigskip
\item Simon said math was the hardest subject \underline{for both he and his brother.}
\begin{enumerate}[label=(\Alph*)]
\item for both he and his brother.
\item for himself and also his brother.
\item for both he and also for his brother.
\item for both him and his brother.
\item for both he and hard also for his brother.
\end{enumerate}
\end{enumerate}