\chapter{Sentence Completions}
\section{SAT Worksheet 1E: Warm-up}
\textit{Directions: Brainstorm the thesis and examples that you would use in the following SAT essay assignment.}

\textit{``Education is the most powerful weapon which you can use to change the world."}
-Nelson Mandela

\bigskip
\textbf{Assignment:} Is education the best way to bring about social change or is it secondary to other approaches?  Plan and write an essay in which you develop your point of view on this issue.  Support your position with reasoning and examples taken from your reading, studies, experience, or observations.

\vfill
\newpage

\section{Sentence Completions}
There are 19 Sentence Completion questions on the SATs.  You get one point for each correct answer, minus ¼ point for each incorrect answer, and no points for answers left blank. Each Sentence Completion question has one blank or two blanks and asks you to choose the word(s) that best fits the meaning of the sentence as a whole.  Each sentence should take less than a minute to answer.

\bigskip
To answer these questions, you need to know the definitions of the vocabulary words, as well as how the words are used in the context of the sentence.  Understanding sentence logic and studying vocabulary is key to doing well on Sentence Completions.  

\bigskip
Each sentence completion will give you at least one clue as to what word belongs in the blank. For example, some sentence completion questions contain two clauses, separated by a comma (,), semicolon (;), or a colon (:).  One clause has the blanks, while the other provides a definition with descriptions or synonyms.

\bigskip
Transition words (like but, although, however, yet, even though) are very important.  They indicate a shift in ideas.  

\bigskip
For example:  Although the film showed scenes of \underline{violence}, its ultimate message was one of \underline{peace}.  

\bigskip
\textit{In this example, what does the transitional word \textit{although} indicate about the relationship between the two vocabulary words, “violence” and “peace”?}

\textbf{There are 4 commonly used types of sentence completions:}
\begin{enumerate}
\item \longline which describes a word and wants you to choose the word from the answer choices.
\item \longline which wants you to look for antonyms or descriptions that give the opposite meaning to the answers. Signal words for this type includes:

\longline, \longline, \longline,

\longline, \longline.
\item \longline which establishes a causal relationship between the two parts of the sentence. Signal words for this type includes: \longline,

\longline, \longline,

\longline, \longline.
\item \longline, which wants you to find a similar word for the words given. Signal words for this type includes: \longline, \longline, and \longline.
\end{enumerate}

\bigskip
\textbf{Definitional:}\\
Some cynics think that America is an \longline, a power structure in which a relative few rule the entire nation.

\bigskip
We are looking for a word whose definition is ``a power structure in which a relative few rule the entire nation."\\
The answer could be ``oligarchy."

\bigskip
\textbf{Contrast:}\\
The students worked \longline, helping one another to complete their projects.

\bigskip
In this example, the clauses are separated by a comma.  The second clause describes how the students were working.  It gives a definition.  The blank needs a word that means the students were helping one another.  
The answer could be a word like cooperatively or collaboratively.  

\bigskip

\textbf{Cause and Effect:}\\
After several inconclusive and unpredictable experiments, the scientist had to admit he was \longline about the effects of the new medicine.

\bigskip
Since the experiments did not prove anything and had unpredictable outcomes, the scientist cannot be certain about the medicine's effects.
The answer could be something like ``uncertain" or ``unsure."

\bigskip
\textbf{Synonyms:}\\
Both \longline and \longline, Brenda could always be found talking and laughing.

\bigskip
This example also provides a description or definition.  Keep in mind parallel structure.  The first blank should have something to do with Brenda always talking, while the second goes with her laughing.  
The answers could be something like ``chatty and good-humored."

\vfill
\newpage

\section[Practice]{SAT Worksheet 2E: Multiple Choice Exercise}
\textit{Directions: Use your vocabulary words and words from chapter 16 to create your own sentence completion multiple choice questions for \#1 and \#2 below. Remember that even the incorrect answer choices should be reasonable. Then, have a partner try to select the correct answer choices. }

\bigskip
\begin{enumerate}
\item Although to most people bungee jumping is \longline, Edward, an extreme risk-taker, found it \longline.
\begin{enumerate}[label=(\Alph*)]
\item
\item
\item
\item
\item
\end{enumerate}

\item{Although the media's coverage has been \longline, the event was actually very sophisticated.}
\begin{enumerate}[label=(\Alph*)]
\item
\item
\item
\item
\item
\end{enumerate}
\end{enumerate}
\pagebreak

\section[Strategies]{Strategies for Completing Sentence Completions}

\begin{enumerate}
\item{Read the \longline. Look for \longline and words that \longline or are \longline or

\longline of the word that goes in the blank. The goal of this is to figure out the relationship between the \longline and the rest of the sentence.}

\bigskip
Then, write your \longline in the blank. You will try to match this to the answer choices.

\bigskip
\textbf{But what should you do if can't figure out your own word to put in the blank?}

\bigskip
{If you need help writing a word to go in the blank, try to determine what

\longline of sentence completion it is. This can then help you identify \longline words. You can also evaluate the \longline of the word by asking yourself, ``Should a positive-, negative- or neutral-sounding word go in the blank?''}

\item{Read the answer choices and \longline the answers that you know are wrong, either because you know the definition of the word or because it has the incorrect \longline.}\\  Afterwards, mark the \longline that is closest to the word you had in the blank.

\textbf{But what should you do if you don't know the meaning of one or more of the answer choices?}

\begin{enumerate}[label=(\Alph*)]
\item Determine if the word in the blank should have a \longline,

\longline, or \longline connotation. Then, determine the \longline of each of the answer choices and

\longline the ones that have the wrong connotation.

\item To figure out the definition of an unfamiliar word, think about where you may have seen or \longline it used before. This will help you to define the word or label a connotation.

\item You can also use \longline, \longline, or

\longline to get an idea of what the unfamiliar word means.

\item If you can not eliminate two or more of the answer choices, then you should

\longline it and come back to it later.
\end{enumerate}

\item{If there is a sentence completion question with \longline blanks, use the strategies in steps 1-2 to \longline and then eliminate words for the \longline blank. With the answer choices remaining, use the strategies in steps 1-2 to create your own word for the blank and  \longline eliminate words for the second blank.}

\bigskip
There should be \longline answer choice remaining. If there is more than one answer choice remaining, try using the strategies in step 2 to try to eliminate the incorrect answers. 
\end{enumerate}
\pagebreak

\section[Strategies]{Summary: Sentence Completion Strategies}

\begin{itemize}
\item The clauses in one sentence completion sentences may have similar meanings or contrasting, conflicting meanings.  Look for these relationships to determine what words best fit the blanks.
\vfill\item If you find that you're thinking of lots of ways to justify your answer, it may be incorrect.  Though Sentence Completions can be wordy, they are usually pretty straightforward.
\vfill\item Focus on descriptive words.  If you are looking for an adjective, what are the other adjectives (or modifiers) in the sentence?
\vfill\item Identify clue words.  Do words like although, but, however, yet, even though indicate that the two clauses have contrasting or conflicting meanings?
\vfill\item Cross out answers that are obviously wrong.
\vfill\item Above all, learn your vocabulary.  The SATs strongly emphasize vocabulary.  Your understanding of word definitions is key to doing well on Sentence Completion questions.
\end{itemize}

\vfill
\newpage

\section[Practice]{SAT Worksheet 3E: Sentence Completion Practice}
\textit{Directions on the SATs: Each sentence below has one or two blanks, each blank indicating that something has been omitted.  Beneath the sentence are five words or sets of words labeled A through E.  Choose the word or set of words that, when inserted in the sentence, best fits the meaning of the sentence as a whole.}

\begin{enumerate}
\item The biography is so \longline that it leaves almost no part of the president's life unexamined.
\begin{enumerate}[label=(\Alph*)]
\item inaccessible
\item complimentary
\item comprehensive
\item circumscribed
\item subjective
\end{enumerate}

\bigskip
\item The professor's references were so obscure and \longline that none of her students were familiar with them.
\begin{enumerate}[label=(\Alph*)]
\item dubious
\item esoteric
\item straightforward
\item irrefutable
\item diaphanous
\end{enumerate}

\bigskip
\item Behavioral scientist Ivan Pavlov did experiments with dogs to demonstrate that a given \longline can elicit a given \longline; for example, ringing a bell to announce dinner caused the dogs to salivate.
\begin{enumerate}[label=(\Alph*)]
\item expectation \ldots loyalty
\item domination \ldots anticipation
\item negotiation \ldots concession
\item aloofness \ldots acknowledgment
\item stimulus \ldots response 
\end{enumerate}

\newpage
\item After his early financial success, Daniel adopted a \longline  manner; he acted superior to even his closest friends.
\begin{enumerate}[label=(\Alph*)]
\item supercilious
\item extroverted
\item euphoric
\item censorious
\item inconspicuous
\end{enumerate}

\bigskip
\item While he started at the company \longline and unsure of himself, he became increasingly \longline as he succeeded at board meetings and presentations.
\begin{enumerate}[label=(\Alph*)]
\item spontaneous \ldots prepared
\item provocative \ldots conciliatory
\item pedestrian \ldots simple
\item diffident \ldots confident  
\item brash \ldots cowed
\end{enumerate}

\bigskip
\item Although the novel met great commercial success, critics and readers alike agreed that the quality of the prose itself was \longline and \hrulefill.
\begin{enumerate}[label=(\Alph*)]
\item pedestrian \ldots derivative
\item groundbreaking \ldots tedious
\item revolutionary \ldots unprecedented
\item courageous \ldots successful 
\item eloquent \ldots ornamental
\end{enumerate}

\bigskip
\item The professor's \longline voice and penchant for \hrulefill

always put me to sleep; I couldn't stay focused on his rambling lectures.
\begin{enumerate}[label=(\Alph*)]
\item melodious \ldots succinctness
\item sonorous\ldots verbosity
\item stimulating \ldots obscurity
\item pugnacious \ldots criticism 
\item toneless \ldots theatricality
\end{enumerate}

\bigskip
\item Connecticut-born army general Benedict Arnold's defection to the British Army during the American Revolution means his name will forever be associated in the minds of Americans with \longline.
\begin{enumerate}[label=(\Alph*)]
\item indigence
\item tenacity
\item equivocation
\item intrepidity
\item perfidy
\end{enumerate}

\bigskip
\item Having published dozens of novels and other works, Philip Roth is an author who writes with almost unmatched \longline.
\begin{enumerate}[label=(\Alph*)]
\item trepidation
\item certitude
\item celerity
\item serendipity
\item lethargy
\end{enumerate}

\bigskip
\item Although Krista had the desire to travel everywhere, she had to acknowledge her limited budget and find a destination that was \longline based on travel costs.
\begin{enumerate}[label=(\Alph*)]
\item feasible
\item impractical
\item precarious
\item innovative
\item exotic
\end{enumerate}

\bigskip
\item The movie critic complained that the new romantic comedy was utterly \hrulefill;

the plot didn't \longline  in any way from the usual clich\'es. 

\begin{enumerate}[label=(\Alph*)]
\item predictable \ldots adhere
\item ironic \ldots depart
\item spellbinding \ldots escape
\item controversial \ldots digress
\item formulaic \ldots deviate 
\end{enumerate}

\bigskip
\item Scientists have bleakly described the earth's oceans as ``plastic soup," filled with bottles, bags, appliances, and other environmentally destructive \longline.
\begin{enumerate}[label=(\Alph*)]
\item decimation
\item raiment
\item malefactors
\item flotsam
\item fetters
\end{enumerate}

\bigskip
\item Hundreds of years ago, many scientists accepted the now \longline idea of ``spontaneous generation," which stated that organisms could arise from non-living matter, i.e. maggots could arise from old meat.

\begin{enumerate}[label=(\Alph*)]
\item modern
\item obsolete
\item nefarious
\item cynical
\item obsequious
\end{enumerate}

\bigskip
\item Based on current market trends, the consultants \longline the future success of the product and presented their conclusions with graphs and other visual aids.
\begin{enumerate}[label=(\Alph*)]
\item scrutinized
\item idealized
\item criticized
\item extrapolated
\item retrieved
\end{enumerate}

\bigskip
\item To dismantle an unjust system, people must actively oppose it.  Simply opting out is a form of passive support; it \longline the status quo by allowing it to continue unchallenged.
\begin{enumerate}[label=(\Alph*)]
\item restricts
\item perpetuates
\item idolizes
\item admires
\item jeopardizes
\end{enumerate}

\newpage
\item While Ray is known for his \longline, his younger brother is quite

\longline, speaking rarely and choosing his words with great care.

\begin{enumerate}[label=(\Alph*)]
\item verbosity \ldots garrulousness
\item generosity \ldots saturnine
\item cynicism \ldots optimism
\item chattiness \ldots aggressive
\item loquaciousness \ldots laconic
\end{enumerate}

\bigskip
\item The water in the cheap motel's pool was anything but \longline; it looked as though it hadn't been cleaned in years.
\begin{enumerate}[label=(\Alph*)]
\item murky
\item limpid
\item gelid
\item contaminated
\item mellifluous
\end{enumerate}

\bigskip
\item Nora had great \longline deciding on her major, because her academic interests were so \longline; she enjoyed taking classes from a large variety of subjects and departments.
\begin{enumerate}[label=(\Alph*)]
\item difficulty \ldots multifaceted
\item trouble \ldots narrow
\item jubilation \ldots unambiguous
\item gratification \ldots nonexistent
\item anxiety \ldots tepid
\end{enumerate}

\newpage
\item Although Scrooge starts as a \longline character, unwilling to share even a penny of his fortune, he becomes \longline after his transformative experiences with the Ghosts of Christmas Past, Present, and Future.
\begin{enumerate}[label=(\Alph*)]
\item generous \ldots jittery
\item parsimonious \ldots penurious
\item covetous \ldots capricious
\item miserly\ldots munificent
\item irritable \ldots lively
\end{enumerate}

\bigskip
\item A \longline professional, the actor knew all his lines from the beginning and delivered a \longline performance that made him a worthy candidate for an Oscar.

\begin{enumerate}[label=(\Alph*)]
\item talented \ldots derivative
\item questionable \ldots noteworthy
\item consummate \ldots superlative
\item multifarious \ldots diverse
\item celebrated \ldots destabilizing
\end{enumerate}
\end{enumerate}
